Paradigms in Physics 2.0

### 2017-06-27 paper.tex
fix typo

\section{Paradigms 2.0 process}
\emph{How did we do it?}

@@

We propose a course that explicitly focuses on physics majors'
mathematical fluency and sense- making skills. Introductory courses
begin to develop these aspects, but the primary goals of those courses
tend to be for students to apply simple concepts (Newton's Laws,
energy conservation, etc.)  to relatively straightforward and very
idealized problems.

This course will be taken just after the introductory physics
sequence. It will leverage students' understandings of simple
mechanical systems from introductory physics to develop their
mathematical fluency in the context of less idealized, more
sophisticated systems. Each physics topic (velocity-dependent forces,
Lagrangian mechanics, Hamiltonian mechanics, special relativity) will
focus on specific math methods (e.g. differential equations, calculus
of variations, generalized coordinates, Legendre transformations,
linear transformations, hyperbola geometry) and will explicitly
feature strategies to make physical sense of mathematics (symbolic
problem solving, reading equations like sentences, making
idealization, coordinating representations, limiting case analysis,
dimensional checking).

@@

\section{Future research}
\emph{Document learning trajectories, new courses.  pre-/post-,
  understanding sense-making.}

@@

\section{Conclusions}
\emph{We made some changes, and the process went well.}

\acknowledgments{Put references below the acknowledgements (and appendixes, if any).}

>>>>

\section{Paradigms 2.0 process}
We began the Paradigms 2.0 process in the Winter of 2016, having in
the previous year obtained faculty agreement, and support from our
Department head.  The process was spearheaded by a committee of four
(the authors DR, LG, EM, and CAM, with EvZ present at meetings
documenting our process).  During the Winter quarter, we informed the
community of our process through a colloquium, and collected student
and faculty perspectives on the existing curriculum.  We then
interviewed faculty who recently taught each of our existing courses
to document topics that were currently covered.  This resulted in a
total of XXX index cards in YYY stacks, corresponding to courses, with
cards color coded by broad topic.

The committee met for ??? weeks to discuss existing challenges and
sort the cards into new stacks corresponding to new and reordered
courses.  When we discussed major changes to a course, we often
invited interested faculty to join us to provide their own perspective
on possible challenges and improvements.  Once we had a draft
proposal, we began inviting each faculty member in to see the cards
and discuss the proposed sequence of courses.  In addition, we had a
meeting with all the current students to explain the proposed changes
and request feedback.

When we had obtained feedback from the entire faculty, we scheduled
\emph{two} faculty meetings (DURATION?).  In the first meeting, we
presented our proposal in detail.  This was needed for several
reasons.  Those faculty we met with first may not have seen the final
proposal.  Some faculty during their individual meetings chose to
focus on a small subset of the curriculum, often relating to courses
they had themselves taught.  In one meeting we presented the proposal
and fielded questions.  In a second faculty meeting, we again
presented our proposal, and

\emph{How did we do it?}

@@

We propose a course that explicitly focuses on physics majors'
mathematical fluency and sense-making skills. Introductory courses
begin to develop these aspects, but the primary goals of those courses
tend to be for students to apply simple concepts (Newton's Laws,
energy conservation, etc.) to relatively straightforward and very
idealized problems.

This course is taken either just after or concurrently with the last
quarter of the introductory physics sequence. It leverages students'
understandings of simple mechanical systems from introductory physics
to develop their mathematical fluency in the context of less
idealized, more sophisticated systems. Each physics topic
(velocity-dependent forces, Lagrangian mechanics, Hamiltonian
mechanics, special relativity) will focus on specific math methods
(e.g. differential equations, calculus of variations, generalized
coordinates, Legendre transformations, linear transformations,
hyperbola geometry) and will explicitly feature strategies to make
physical sense of mathematics (symbolic problem solving, reading
equations like sentences, making idealization, coordinating
representations, limiting case analysis, dimensional checking).

@@

\emph{Future research: Document learning trajectories, new courses.  pre-/post-,
  understanding sense-making.}

@@

\acknowledgments{This paper is based upon work supported by the
  National Science Foundation under Grant No. 1323800 Supplement.}
